Particle Interception as a Function of Reynolds Number and Collector Density

### 2020-10-17 code/analysis.Rmd
monte carlo figure added
latest code
added hline and asterisks

library(tidyverse)

@@

reps = 10000

@@

p_phi <- lmsphi %>%
  ggplot(aes(x = paste0(100*as.numeric(phi),"%"), y = avg, ymin = avg-1.96*sd, ymax = avg+1.96*sd)) +
  geom_point() +
  geom_errorbar() +
  theme_bw() +
  ylim(-3,1.5) +
  xlab(expression(paste("Solid volume fraction (",phi,")"))) +
  ylab(expression(paste("Effect size: ",beta[log(Re)])))

p_re <- lmsre %>%
  ggplot(aes(x = as.factor(round(as.numeric(Re),0)), y = avg, ymin = avg-1.96*sd, ymax = avg+1.96*sd)) +
  geom_point() +
  geom_errorbar() +
  theme_bw() +
  ylim(-3,1.5) +
  xlab(expression(Re[c])) +
  ylab(expression(paste("Effect size: ",beta[log(phi)])))

plot_grid(p_re, p_phi, labels = c("(a)","(b)"), scale = .9)

>>>>

library(tidyverse)
library(broom)
library(cowplot)
library(lme4)

@@

reps = 30000

@@

p_phi <- lmsphi %>%
  ggplot(aes(x = paste0(100*as.numeric(phi),"%"), y = avg, ymin = avg-1.96*sd, ymax = avg+1.96*sd)) +
  geom_point() +
  geom_errorbar() +
  geom_hline(yintercept = 0, lty = 2) +
  theme_bw() +
  geom_text(aes(y = avg + 1.96*sd + 1, label = c("*",NA,"*")), fontface = "bold", size = 5) +
  ylim(-3,1.5) +
  xlab(expression(paste("Solid volume fraction (",phi,")"))) +
  ylab(expression(beta[log(Re)]))

p_re <- lmsre %>%
  ggplot(aes(x = as.factor(round(as.numeric(Re),0)), y = avg, ymin = avg-1.96*sd, ymax = avg+1.96*sd)) +
  geom_point() +
  geom_errorbar() +
  geom_hline(yintercept = 0, lty = 2) +
  theme_bw() +
  geom_text(aes(y = avg + 1.96*sd + 1, label = c(NA,"*","*")), fontface = "bold", size = 5) +
  ylim(-3,1.5) +
  xlab(expression(Re[c])) +
  ylab(expression(beta[log(phi)]))

monteplot <- plot_grid(p_re, p_phi, labels = c("(a)","(b)"), scale = .9)

monteplot

save_plot("../pics/montecarlo.png", monteplot, dpi = 600)
